Recent Advances in Networking

### 2013-07-24 Compiled/ebook.tex
fixes
common latex and bibtex styles for all chapters
added page numbers and initial support for copyright, urls are now clickable

%styles

@@

@@

@@

\maketitle

@@

@@

\includepdf[pages=-]{chapter1/chapter1.pdf}
\includepdf[pages=-]{chapter2/chapter2.pdf}
\includepdf[pages=-]{chapter3/chapter3.pdf}
\includepdf[pages=-]{chapter4/chapter4.pdf}
\includepdf[pages=-]{chapter5/chapter5.pdf}
\includepdf[pages=-]{chapter6/chapter6.pdf}
\includepdf[pages=-]{chapter7/chapter7.pdf}
\includepdf[pages=-]{chapter8/chapter8.pdf}
\includepdf[pages=-]{chapter9/chapter9.pdf}

>>>>

%styles
\input{commonstyle}

%\hypersetup{pdftitle={Recent Advances in Networking},\
%           pdfauthor={Hamed Haddadi and Olivier Bonaventure (Editors)}}

@@

%\includepdfset{pagecommand=\thispagestyle{plain}}

@@

\author{
Hamed Haddadi,  Olivier Bonaventure (Editors)\\
}

@@

\date{August 2013}

\maketitle
\pagenumbering{roman}

@@

\pagenumbering{arabic}

@@

\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter1/chapter1.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter2/chapter2.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter3/chapter3.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter4/chapter4.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter5/chapter5.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter6/chapter6.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter7/chapter7.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter8/chapter8.pdf}
\includepdf[pages=-,pagecommand=\thispagestyle{plain}]{chapter9/chapter9.pdf}
